Fixing Vulnerabilities Hinders Maintainability

### 2019-02-03 paper/ICPC19/icpc19.tex
fix luis

\luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}

@@

\luis{many directions such as -> many directions:}
\luis{evaluate the impact of programming languages of the
maintainability of each refactoring pattern; - > evaluate the impact of each refactoring pattern on the maintainbility of each  }

>>>>

\Luis{secure security frameworks, nao percebi bem o que se quer dizer aí.}

@@

\Luis{many directions such as -> many directions:}
\Luis{evaluate the impact of programming languages of the
maintainability of each refactoring pattern; - > evaluate the impact of each refactoring pattern on the maintainbility of each  }
